---
title: "Lab Version - Analyzing HOBO Tempo Data"
author: "Connor Flynn"
date: "10/19/2022"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

#load libraries
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

librarian::shelf(tidyverse,
                here,
                janitor,
                lubridate,
                plotly,
                RColorBrewer)

```

Read in HOBO temperature data

```{r}
bb_data <- read_csv(here("data/June_October_2022_Fishponds/BB_20970109.csv"))

gg_data <- read_csv(here("data/June_October_2022_Fishponds/GG_20970122.csv"))
  
o_data <- read_csv(here("data/June_October_2022_Fishponds/O_20970093.csv"))

oyg_data <- read_csv(here("data/June_October_2022_Fishponds/OYG_20970123.csv"))
  
# IN-LAB CODE

# Here we have imported 4 of the 5 datasets into our environment. Can you use the code above to import the last remaining dataset from the "data/June_October_2022_Fishponds" folder?
  
```






Clean Column Names

```{r}
bb_data <- bb_data %>% 
  clean_names

gg_data <- gg_data %>% 
  clean_names

o_data <- o_data %>% 
  clean_names

oyg_data <- oyg_data %>% 
  clean_names

yg_data <- yg_data %>% 
  clean_names


```



Merge Date and Time Columns

```{r}
bb_data$date_time = dmy_hms(paste(bb_data$date, bb_data$time))

gg_data$date_time = dmy_hms(paste(gg_data$date, gg_data$time))

o_data$date_time = dmy_hms(paste(o_data$date, o_data$time))

oyg_data$date_time = dmy_hms(paste(oyg_data$date, oyg_data$time))

yg_data$date_time = dmy_hms(paste(yg_data$date, yg_data$time))


```



Add Location Column

```{r}
bb_data$location = "bb"

gg_data$location = "gg"

o_data$location = "o"

oyg_data$location = "oyg"

# IN-LAB CODE

# We have added location columns to 4 of the 5 dataframes. Can you use the code above to add a location column to the last remaining dataframe (yg_data)



```



Create a List of Dataframes to Join

```{r}
df_list <- list(bb_data, gg_data, o_data, oyg_data, yg_data)
```


Combine Dataframes in List

```{r}
all_data <- Reduce(function(x, y) merge(x, y, all=TRUE), df_list, accumulate=FALSE)
```


Plot Data

```{r}
ggplot(data = all_data, aes(x = date_time, y = temp_c_c_1, colour = location))+
  geom_line() +
  theme_minimal()



```



Trim ends 


```{r}
all_data_trimmed <- all_data[all_data$date_time > "2022-06-11" &    # Extract data frame subset
                   all_data$date_time < "2022-10-5", ]
```


```{r}
ggplot(data = all_data_trimmed, aes(x = date_time, y = temp_c_c_1, colour = location))+
  geom_line() +
  theme_minimal()
```

Facet (separate) by Location

```{r}
ggplot(data = all_data_trimmed, aes(x = date_time, y = temp_c_c_1, colour = location))+
  geom_line() +
  theme_minimal() + 
  facet_wrap(~location)
```

Add Regression Lines

```{r}
plot <- ggplot(data = all_data_trimmed, aes(x = date_time, y = temp_c_c_1, colour = location))+
  geom_line() +
  theme_minimal() + 
  facet_wrap(~location) +
  geom_smooth(method = "lm")

plot
```


Make Interactive with the Plotly Package

```{r}
ggplotly(plot)
```

Breakdown Dates and Times to take a Look at Range

Seperate Date and Time Columns

```{r}
all_data_trimmed_sep_date_time <- all_data_trimmed %>%
  tidyr::separate('date_time',
                  into = c('date_new', 'time_new'),
                  sep= ' ',
                  remove = FALSE)
head(all_data_trimmed_sep_date_time)
```



Separate Year, Month, and Day Columns
```{r}
all_data_trimmed_sep_date <- all_data_trimmed_sep_date_time %>%
  tidyr::separate('date_new',
                  into = c('year', 'month', 'day'),
                  sep= '-',
                  remove = FALSE)
head(all_data_trimmed_sep_date)
```


Group Data to Find Daily Min and Max Temperatures for Range

```{r}
all_data_range <- all_data_trimmed_sep_date %>%
  group_by(year, month, day, location, date_new)%>%
  summarise(min_temp = min(temp_c_c_1), max_temp = max(temp_c_c_1))%>%
  mutate(range = max_temp-min_temp)

head(all_data_range, digits=20)
```


Plot Daily Temperature Ranges for Each Location

```{r}
ggplot(data=all_data_range, 
                   aes(x=as.Date(date_new, format = "%Y - %m - %d"), 
                       y=range, colour=location)) +
   


  geom_smooth()+
  theme_minimal()+
  theme(axis.text.x = element_text(margin = margin(t=5)))+
  labs(title="Daily temperature range", y="Mean daily temperature range (°C) with 95% CI ", x="Date")+
  scale_color_brewer(palette="Set3") 
```


